Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-07-17 STAT-paper-template/APA/fertile.Rnw
added file path checks subsection

<<proj_check_some>>=
proj_check_some(proj_dir, contains("paths"))
@

@@

\subsubsection{File Type Checks}

@@

<<paths, message=FALSE>>=
is_path_portable("~")
@

@@

\subsubsection{Package Features}

>>>>

<<proj_check_some, warning = FALSE>>=
proj_check_some(proj_dir, contains("paths"))
@

@@

\subsubsection{File Paths}

For users focused on file paths, the \func{check\_path()} function analyzes a vector of paths (or a single path) to determine whether there are any absolute paths or paths that lead outside the project directory.

<<path checks, error = TRUE>>=

# Path inside the directory
check_path("project_miceps")

# Absolute path (current working directory)
check_path(getwd())

# Path outside the directory
check_path("../fertile.Rmd")

@

\subsubsection{File Types}

@@

@@
